---
title: "RT Overview"
author: "Irene Steves and Bryce Mecum"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
# knitr::opts_chunk$set(eval = FALSE)
library(knitr)
library(kableExtra)

format_result <- function(query_result) {
  result <- knitr::kable(query_result, format = "html")

  kableExtra::kable_styling(result,
                            bootstrap_options = c("striped",
                                                  "hover",
                                                  "condensed"))

  kableExtra::scroll_box(result,
                         width = "100%",
                         height = "400px") #display concisely

  result
}
```

Searching through RT requires some knowledge of how RT does queries. This vignette provides a basic introduction to RT's query syntax and some examples of how to make queries with this package. Best Practical's [Query Builder documentation](https://docs.bestpractical.com/rt/4.4.0/query_builder.html) and [Ticket SQL wiki page](https://rt-wiki.bestpractical.com/wiki/TicketSQL) highlight some of the key aspects of query-building and are useful to reference while learning.

## Writing a query

The `rt_ticket_search` function makes it easy to search through your tickets. These are the fields that it will return by default, and that you can use to search with:

```{r default-fields, echo = FALSE}
c("AdminCc", "Created", "Creator", "Due", "FinalPriority", "id", "InitialPriority", "LastUpdated", "Owner", "Priority", "Queue", "Requestors", "Resolved", "Started", "Starts", "Status", "Subject", "TimeEstimated", "TimeLeft", "TimeWorked", "Told", "CF.{NAME_OF_CUSTOM_FIELD}")
```

There are additional queryable fields such as `FileName`, `ContentType`, and `Content`, `Requestor.Name` that you can explore in the [Query Builder](https://docs.bestpractical.com/rt/4.4.0/query_builder.html) (Search --> Tickets --> New Search). 

These fields are some of the most commonly queried:

- **id** - the ticket #
- **Subject** - the subject of the ticket
- **Owner** - the current owner of the ticket
- **Queue** - the queue(s) you want to search through
- **Content** - the text content of your RT tickets (email correspondence, comments, etc.); _note:_ unless the full-text indexing feature is enabled, you will only be able to search through the metadata of your tickets
- **FileName** - the name of an attached file

To build a query, you'll want to use the following vocabulary:

- `AND` or `OR` to join multiple query conditions together
- `=` to specify that a field `is` or is `equal to` something
- `!=` to specify that a field `is not` or is `not equal to` something
- `<` or `>` to specify that a field `less than` (`before`) or `greater than` (`after`) something
- `LIKE` to specify that a field `matches` something
- `NOT LIKE` to specify that a field `doesn't match` something

## Setup

Before we can run queries, we need to load the `rt` package and provide basic details about the RT installation we want to query.
Best Practical (who makes RT) provide a demonstration RT installation that we'll be using for this vignette but in all likelihood you'll be using different values in your scripts.

```{r load-and-connect, message = FALSE}
library(rt)

Sys.setenv(RT_BASE_URL = "http://localhost:8080") # Your RT installation's URL (where you log in)
rt_login(user = "root", pass = "password") # Or use rt_login_interactive()
```

## Example queries

To search for all tickets in the "General" queue, we'd run the following:

```{r first-query}
result <- rt_ticket_search("Queue = 'General'")
```

By default, `rt_ticket_search` returns a list with names `content`, `path`, and `response`. Also by default, `result$content` will be a turned into a `data.frame` or `tibble` (if installed). Let's look at that in a formatted table:

```{r formatted-first-query, echo = FALSE}
format_result(result$content)
```

You can search against multiple fields using `AND` or `OR` to combine them.

```{r query-and, eval = FALSE}
result <- rt_ticket_search("Queue = 'General' AND Subject LIKE 'test'")
```

Use parentheses to group query parameters together for more advanced logic.

```{r query-parens, eval = FALSE}
result <- rt_ticket_search("(Status = 'new' OR Status = 'open') AND Queue = 'General'")
```

For numeric and date/time fields, you can use `>`, `>=`, `<`, and `<=` in addition to `=`.

```{r query-dates, eval = FALSE}
result <- rt_ticket_search("Created > '2018-04-04'")
```

You can also use special [date syntax](https://rt-wiki.bestpractical.com/wiki/TicketSQL#Date_Syntax) for more options.

```{r query-dates-special, eval = FALSE}
result <- rt_ticket_search("Created >= '2 days ago'")
```

## Common use-cases

One of the most common use-cases is searching through RT ticket content. 

```{r query-like, eval = FALSE}
result <- rt_ticket_search("Content LIKE 'Can you please advise'")
```
