---
title: "Searching RT"
author: "Irene Steves"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
# knitr::opts_chunk$set(eval = FALSE)
library(knitr)
library(kableExtra)

format_result <- function(query_result) {
  query_result %>% 
    knitr::kable(format = "html") %>% 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>% 
    kableExtra::scroll_box(width = "100%",
                           height = "400px") #display concisely
}
```

Searching through RT requires some knowledge of queries, but it's easy to do once you understand the syntax and have some examples to work off of. Best Practical's [Query Builder documentation](https://docs.bestpractical.com/rt/4.4.0/query_builder.html) and [Ticket SQL wiki page](https://rt-wiki.bestpractical.com/wiki/TicketSQL) highlight some of the key aspects of query-building. In this vignette, I've included some of common query examples.

## Set-up

Load the `rt` package and connect with your RT instance.

```{r message = FALSE}
library(rt)

options(rt_base = "https://demo.bestpractical.com/") #set your server name
rt_login(user = "guest", pass = "guest") #generally, you'd use rt_login_interactive()
```

## Writing a query

The `rt_ticket_search` function makes it easy to search through your tickets. These are the fields that it will return by default, and that you can use to search through.

```{r echo = FALSE}
c("AdminCc", "Created", "Creator", "Due", "FinalPriority", "id", "InitialPriority", "LastUpdated", "Owner", "Priority", "Queue", "Requestors", "Resolved", "Started", "Starts", "Status", "Subject", "TimeEstimated", "TimeLeft", "TimeWorked", "Told", "CF.{NAME_OF_CUSTOM_FIELD}")
```

There are additional query-able fields such as `FileName`, `ContentType`, `Content`, `Requestor.Name` that you can explore in the [Query Builder](https://docs.bestpractical.com/rt/4.4.0/query_builder.html) (Search --> Tickets --> New Search). 

These fields are some of the most commonly queried:

- **id** - the ticket #
- **Subject** - the subject of the ticket
- **Owner** - the current owner of the ticket
- **Queue** - the queue(s) you want to search through
- **Content** - the text content of your RT tickets (email correspondence, comments, etc.); _note:_ unless the full-text indexing feature is enabled, you will only be able to search through the metadata of your tickets
- **FileName** - the name of an attached file

To build a query, you'll want to use the following vocabulary:

- `AND` or `OR` to join multiple query parameters together
- `=` to specify that a parameter `is` or is `equal to` something
- `!=` to specify that a parameter `is not` or is `not equal to` something
- `<` or `>` to specify that a parameter `less than` (`before`) or `greater than` (`after`) something
- `LIKE` to specify that a parameter `matches` something
- `NOT LIKE` to specify that a parameter `doesn't match` something

## Example queries

To search through your tickets, input your query as a string (enclose it in quotes). 

```{r}
result <- rt_ticket_search(query = "Queue = 'General'")
```

```{r echo = FALSE}
format_result(result$content)
```

You can search multiple parameters using `AND` or `OR` to combine them.

```{r eval = FALSE}
result <- rt_ticket_search("Queue = 'General' AND Subject LIKE 'test'")
```

Use parentheses to group query parameters together.

```{r eval = FALSE}
result <- rt_ticket_search(query = "(Status = 'new' OR Status = 'open') AND Queue = 'General'")
```

For numeric and date/time fields, you can use `>`/`>=`/`<`/`<=` in addition to `=`.

```{r eval = FALSE}
result <- rt_ticket_search("Created > '2018-04-04'")
```

You can also use special [date syntax](https://rt-wiki.bestpractical.com/wiki/TicketSQL#Date_Syntax) for more options.

```{r eval = FALSE}
result <- rt_ticket_search("Created >= '2 days ago'")
```

## Common use-cases

One of the most common use-cases is searching through RT ticket content. 

```{r eval = FALSE}
result <- rt_ticket_search("Content LIKE 'Can you please advise'")

#how to search specific ticket
#ticket history
```
